\documentclass[modern]{aastex61}

\input{stylez}

\begin{document}%\raggedbottom\sloppy\sloppypar\frenchspacing

\setlength{\abovedisplayskip}{1.5em}
\setlength{\belowdisplayskip}{1.5em}

\title{%
    Analytical Transit Light Curves for Limb-Darkened Stars
}

\author[0000-0002-0296-3826]{Rodrigo Luger}
\affil{Department~of~Astronomy, University~of~Washington, Seattle, WA}
\author{Eric Agol}
\affil{Department~of~Astronomy, University~of~Washington, Seattle, WA}

\keywords{methods: analytical --- techniques: photometric}

\begin{abstract}
    We derive analytical, closed form solutions for the light curve
    of a planet transiting a star with a limb darkening profile of
    arbitrary order. We provide updated expressions for the linear
    and quadratically limb darkened cases that are numerically stable
    over the entire domain.
\end{abstract}

% ==============================================================================
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
%
\section{Introduction}
\label{sec:intro}
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
% ==============================================================================

Currently I just copy-pasted some relevant stuff from the \starry paper.
This week I'll organize this into sections and get an outline going.\todo{}

\cite{Gimenez2006} derived transit light curves for a limb-darkening
function
\begin{equation}
I(\mu) = I(1) \left[\sum_{n=1}^N u_n (1-\mu^n) \right],
\end{equation}
where $\mu = \cos{\theta} =\sqrt{1-r^2}$, where $\theta$ is the polar angle measured from the 
sub-observer point), and $u_n$ is a limb-darkening coefficient.  \cite{Gimenez2006}
found an infinite series for computing the limb-darkened light curve for each $u_n$
term.  Here we present closed-form expressions for these terms which can be
easily computed with recursion relations.

\cite{Pal2008} derived the partial derivatives of the quadratic limb-darkening model 
with respect to $b$ and $r$.


% ==============================================================================
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
%
\section{Linear Limb-Darkening}
\label{sec:reparam}
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
% ==============================================================================

From \citet{MandelAgol2002}, the total flux visible during the occultation of a
body whose surface map is given by $I(x, y) = \sqrt{1 - \x^2 -\y^2}$ may be computed
as
%
\begin{align}
    \label{eq:s2}
    s_2 = \frac{2\pi}{3} \left(1 - \frac{3\Lambda}{2} - \Theta(r - b) \right)
\end{align}
%
where $\Theta(\bigdot)$ is the Heaviside step function and $\Lambda$ is given
by \todo{Eric}

% ==============================================================================
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
%
\section{Polynomial Limb-Darkening}
\label{sec:quad}
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
% ==============================================================================

Any radially symmetric specific intensity profile can be expressed as a sum
over the $m = 0$ spherical harmonics.
%
In particular, the radial intensity profile of a quadratically
limb-darkened star,
%
\begin{align}
    \label{eq:quadraticld}
    I(\upmu) &= 1 - u_1 (1 - \upmu) - u_2 (1 - \upmu)^2
    \quad,
\end{align}
%
where $\upmu = \z = \sqrt{1 - \x^2 - \y^2}$ and $u_1$ and $u_2$ are the
limb darkening coefficients, can be written in terms of spherical harmonics
by re-writing \eq{quadraticld} as
%
\begin{align}
    I(\x, \y) = (1 - u_1 - 2u_2) + (u_1 + 2u_2) \z + u_2 \x^2 + u_2 \y^2
           \quad.
\end{align}
%
Performing the change of basis to spherical harmonics \citep{starry}, we have
%
\begin{align}
    \label{eq:qldylm}
    I(\x, \y) =
            \frac{2\sqrt{\pi}}{3} (3 - 3u_1 + 4u_2) \, Y_{0,0}
          + \frac{2\sqrt{\pi}}{\sqrt{3}} (u_1 + 2u_2) \, Y_{1,0}
          - \frac{4\sqrt{\pi}}{3\sqrt{5}} u_2 \, Y_{2,0}
      \quad.
\mathematica{limbdark}
\end{align}
%
Thus, quadratic limb darkening can be expressed exactly as the sum of the first
three $m = 0$ spherical harmonics.

\section{Radius of order impact parameter limit}

In the limit that $\vert b -r\vert \lll 1$, the edge of the occulter passes
over the center of the star.  Round-off error can cause the $s_2$ expression
to have fluctuations in the evaluation of the elliptic integral; this is
due a term that should cancel the step function...
Here we present two series expansions valid
for $\vert \epsilon \vert << 1$, where $\epsilon = b-r$, one of which is valid
for $b+r <1$ and a second for $b+r > 1$.

\subsection{$b+r <1$}

In the limit of $b+r


\bibliography{limbdark}

\end{document}
